---
title: "Dissertation Study Three EDA: Early Dating"
author: "Linh Nguyen"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: 'hide'
---

# I. Meta-Data

In order to replicate this code file, the following files are needed in the directory `data/yw/` found within the project directory: `50130_20100409.sav`, `50130_2_20100409.sav`, `50130_3_20100409.sav`, and `current and cut participants.xlsx`. R code associated with each code chunk can be viewed and hidden by toggling on `Code` on the top right of each output.

```{r setup, results = 'hide', message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
options(digits = 3)

libraries <- c("here",         # directory access
               "labelled",     # spss labels
               "stringr",      # working with strings
               "tidyr",        # pivot_wider
               "rio",          # import export
               "summarytools", # descriptives
               "ggplot2",      # plots
               "kableExtra",   # scroll box
               "forcats",      # fct_reorder for barplot
               "sjPlot",       # plot_grid
               "dplyr",        # general wrangling
               "lmerTest")     # linear mixed models

lapply(libraries, require, character.only = TRUE)
```

```{r session-info, message = FALSE, warning = FALSE, results = "hold"}
# list of loaded packages and versions
si <- devtools::session_info()[[2]]
rownames(si) <- NULL
si %>% 
  select(package, loadedversion, date, source) %>% 
  
  #red bold the called packages
  mutate(package = 
           cell_spec(package, 
                     color = ifelse(package %in% libraries, "red", "black"),
                     bold = ifelse(package %in% libraries, TRUE, FALSE))) %>% 
  knitr::kable(escape = F, caption = "All loaded packages. 
               Bolded in red are those loaded explicitly 
               with <code>library()</code>") %>% 
  kable_styling() %>% 
  scroll_box(height = "300px")
```

## II. Basic Descriptives

```{r data}
# load in dat files
dat_w1 <- rio::import(paste0(here(), "/data/yw/50130_20100409.sav"))
dat_w2 <- rio::import(paste0(here(), "/data/yw/50130_2_20100409.sav"))
dat_w3 <- rio::import(paste0(here(), "/data/yw/50130_3_20100409.sav"))
ids <- rio::import(paste0(here(), "/data/yw/current and cut participants.xlsx")) %>%
  select(couple = `4`, 
         ID = `Survey Code`) %>%
  filter(!is.na(couple) & couple != "XXX") %>%
  mutate(ID = str_remove(ID, "\r\n")) %>%
  # save only IDs that appear in dat_w1, dat_w2, or dat_w3
  filter(ID %in% c(dat_w1$QLogin_1, dat_w2$QLogin_1, dat_w3$QLogin_1))

# fix NA strings
dat_w1[dat_w1==99999999] <- NA
dat_w2[dat_w2==99999999] <- NA
dat_w3[dat_w3==99999999] <- NA

# old sex code: 1 = male 2 = female
# new sex code: 1 = female 2 = male
dat_w1$Qd1 <- as.numeric(dat_w1$Qd1 == 2)
dat_w1$Qd1[dat_w1$Qd1 == 0] <- 2

# age as numeric
dat_w1$Qd3_1 <- as.numeric(dat_w1$Qd3_1)
```

### 1. Dictionary: Scale items and labels

```{r var-names}
# BASIC DEMO AND ID ------------------------------------------------------------
basics <- data.frame(
  var_old = names(dat_w1)[grepl("QLogin_1|Qd.*", names(dat_w1))],
  var_new = c(
    "ID",
    "sex",
    "ethnic_black",
    "ethnic_asian",
    "ethnic_white",
    "ethnic_hisp",
    "ethnic_other",
    "ethnic_other_txt",
    "age",
    "duration",
    "rela_status"
  ),
  labels = var_label(dat_w1[, grepl("QLogin_1|Qd.*", names(dat_w1))], unlist = T),
  row.names = NULL
)
basics %>%
  knitr::kable(
    caption = "Basic identifiers and demographics") %>%
  kable_styling() %>%
  scroll_box(height = "300px")

# BFAS -------------------------------------------------------------------------

# bfas variables for self-report wave 1
bfas_self <- data.frame(
  var_old = names(dat_w1)[grepl("QBFASnIMP.*_A_", names(dat_w1))],
  labels = var_label(dat_w1[,grepl("QBFASnIMP.*_A_", names(dat_w1))], unlist = T),
  row.names = NULL
) %>%
  # remove extra things around the questions
  mutate(labels = str_remove(labels, pattern = " General Question: \\]")) %>%
  mutate(labels = str_remove(labels, pattern = "You \\[")) %>%
  mutate(labels = str_remove(labels, pattern = "[^.]*\\.")) %>%
  mutate(labels = str_remove(labels, pattern = "(\\w+\\s+){1}")) %>%
  mutate(labels = str_remove_all(labels, pattern = "\\."))
bfas_self$var_new <- paste0("bfas_", 1:100)

# bfas variables for self-report longitudinal
bfas_fu <- data.frame(
  var_old = names(dat_w2)[grepl("QOwnPersBFAS.*_A_", names(dat_w2))],
  labels = var_label(dat_w2[,grepl("QOwnPersBFAS.*_A_", names(dat_w2))], unlist = T),
  row.names = NULL
)
# add order to use for arranging after merging
bfas_fu <- bfas_fu %>%
  mutate(order = 1:nrow(bfas_fu)) %>%
  # remove extra things around the questions
  mutate(labels = str_remove(labels, pattern = " General Question: \\]")) %>%
  mutate(labels = str_remove(labels, pattern = " \\[")) %>%
  mutate(labels = str_remove(labels, pattern = "[^.]*\\.")) %>%
  mutate(labels = str_remove(labels, pattern = "(\\w+\\s+){1}")) %>%
  mutate(labels = str_remove_all(labels, pattern = "\\.")) %>%
  merge(subset(bfas_self, select = -var_old), all.x = T, all.y = F, by = "labels") %>%
  arrange(order)
# fix unmatched questions
bfas_fu[grepl("beauty in things that others might not notice", bfas_fu$labels), "var_new"] <- "bfas_100"
bfas_fu[grepl("be bothered with other's needs", bfas_fu$labels), "var_new"] <- "bfas_32"
bfas_fu[grepl("felt depressed", bfas_fu$labels), "var_new"] <- "bfas_41"
bfas_fu[grepl("got irritated", bfas_fu$labels), "var_new"] <- "bfas_16"
bfas_fu[grepl("noticed the emotional aspects of paintings and pictures", bfas_fu$labels), "var_new"] <- "bfas_60"
bfas_fu[grepl("what I started", bfas_fu$labels), "var_new"] <- "bfas_43"
bfas_fu <- bfas_fu %>% select(-c(order))

# bfas variables for other-reports
bfas_partner <- data.frame(
  var_old = names(dat_w1)[grepl("QPartnerBFAS", names(dat_w1))],
  var_new = str_replace(bfas_fu$var_new, "_", "_partner_"),
  labels = str_remove(
    str_remove(
      var_label(dat_w1[, grepl("QPartnerBFAS", names(dat_w1))], unlist= T),
      "General.*"),
    "[^.]*\\."),
  row.names = NULL
)

# double check labels for bfas self and other
bfas_self$labels <- bfas_fu$labels <- NULL
bfas_self$labels <- str_remove(
  str_remove(
    var_label(dat_w1[,grepl("QBFASnIMP.*_A_", names(dat_w1))], unlist = T),
    "General.*"),
  "[^.]*\\.")
bfas_fu$labels <- str_remove(
  str_remove(
    var_label(dat_w2[,grepl("QOwnPersBFAS.*_A_", names(dat_w2))], unlist = T),
    "General.*"),
  "[^.]*\\.")

# keys
bfas_self <- bfas_self %>%
  mutate(keys = ifelse(grepl(
    "_1$|_21$|_41$|_71$|_16$|_36$|_56$|_76$|_2$|_32$|_52$|_62$|_82$|\
    |_17$|_37$|_67$|_77$|_87$|_97$|_13$|_23$|_33$|_53$|_83$|_93$|\
    |_8$|_48$|_68$|_78$|_14$|_24$|_34$|_54$|_64$|_29$|_49$|_79$|_99$|\
    |_15$|_45$|_55$|_85$|_50$|_60$|_80$|_90", var_new),
    -1, 1))
bfas_fu <- bfas_fu %>%
  mutate(keys = ifelse(grepl(
    "_1$|_21$|_41$|_71$|_16$|_36$|_56$|_76$|_2$|_32$|_52$|_62$|_82$|\
    |_17$|_37$|_67$|_77$|_87$|_97$|_13$|_23$|_33$|_53$|_83$|_93$|\
    |_8$|_48$|_68$|_78$|_14$|_24$|_34$|_54$|_64$|_29$|_49$|_79$|_99$|\
    |_15$|_45$|_55$|_85$|_50$|_60$|_80$|_90", var_new),
    -1, 1))
bfas_partner <- bfas_partner %>%
  mutate(keys = ifelse(grepl(
    "_1$|_21$|_41$|_71$|_16$|_36$|_56$|_76$|_2$|_32$|_52$|_62$|_82$|\
    |_17$|_37$|_67$|_77$|_87$|_97$|_13$|_23$|_33$|_53$|_83$|_93$|\
    |_8$|_48$|_68$|_78$|_14$|_24$|_34$|_54$|_64$|_29$|_49$|_79$|_99$|\
    |_15$|_45$|_55$|_85$|_50$|_60$|_80$|_90", var_new),
    -1, 1))

# scale scores
bfas_self <- bfas_self %>%
  mutate(subscale = case_when(
    grepl("1$|6$", var_new) ~ "neuroticism",
    grepl("2$|7$", var_new) ~ "agreeableness",
    grepl("3$|8$", var_new) ~ "conscientiousness",
    grepl("4$|9$", var_new) ~ "extraversion",
    grepl("5$|0$", var_new) ~ "openness"))
bfas_fu <- bfas_fu %>%
  mutate(subscale = case_when(
    grepl("1$|6$", var_new) ~ "neuroticism",
    grepl("2$|7$", var_new) ~ "agreeableness",
    grepl("3$|8$", var_new) ~ "conscientiousness",
    grepl("4$|9$", var_new) ~ "extraversion",
    grepl("5$|0$", var_new) ~ "openness"))
bfas_partner <- bfas_partner %>%
  mutate(subscale = case_when(
    grepl("1$|6$", var_new) ~ "neuroticism",
    grepl("2$|7$", var_new) ~ "agreeableness",
    grepl("3$|8$", var_new) ~ "conscientiousness",
    grepl("4$|9$", var_new) ~ "extraversion",
    grepl("5$|0$", var_new) ~ "openness"))

# print dict
bfas_self %>%
  knitr::kable(
    caption = "BFAS labels and item names for self-report at wave 1") %>%
  kable_styling() %>%
  scroll_box(height = "300px")
bfas_fu %>%
  knitr::kable(
    caption = "BFAS labels and item names for self-reports at waves 2 and 3") %>%
  kable_styling() %>%
  scroll_box(height = "300px")
bfas_partner %>%
  knitr::kable(
    caption = "BFAS labels and item names for partner-reports") %>%
  kable_styling() %>%
  scroll_box(height = "300px")

# AAQ --------------------------------------------------------------------------
# reverse items: 1, 3, 4, 12, 14, 16, 17
aaq_keys <- rep(1, 17)
aaq_keys[c(1, 3, 4, 12, 14, 16, 17)] <- -1

aaq <- data.frame(
  var_old = names(dat_w1)[grepl("QAAQ", names(dat_w1))],
  var_new = paste0("aaq_", 1:17),
  keys = aaq_keys,
  labels = str_remove(
    str_remove(
      var_label(dat_w1[,grepl("QAAQ", names(dat_w1))], unlist = T),
      "General.*"),
    "[^.]*\\."),
  row.names = NULL
)

# scale scores
# avoidance items: 1-3 and 5-9
# anxiety items: everything else
aaq <- aaq %>%
  mutate(subscale = ifelse(grepl("_1$|_2$|_3$|_5$|_6$|_7$|_8$|_9$", var_new),
                           "avoidance",
                           "anxiety"))
# print dict
aaq %>%
  knitr::kable(
    caption = "AAQ labels and item names") %>%
  kable_styling() %>%
  scroll_box(height = "300px")

# Responsiveness ---------------------------------------------------------------
resp <- data.frame(
  var_old = names(dat_w1)[grepl("QResponsiveness", names(dat_w1))],
  var_new = paste0("resp_", 1:18),
  labels = str_remove(
    str_remove(
      var_label(dat_w1[,grepl("QResponsiveness", names(dat_w1))], unlist = T),
      "General.*"),
    "[^.]*\\."),
  row.names = NULL
)
resp %>%
  knitr::kable(
    caption = "Responsiveness labels and item names") %>%
  kable_styling() %>%
  scroll_box(height = "300px")

# Trust ------------------------------------------------------------------------
trust <- data.frame(
  var_old = names(dat_w1)[grepl("Qtrust", names(dat_w1))],
  var_new = paste0("trust_", 1:17),
  labels = str_remove(
    str_remove(
      var_label(dat_w1[,grepl("Qtrust", names(dat_w1))], unlist = T),
      "General.*"),
    "[^.]*\\."),
  row.names = NULL
)
trust %>%
  knitr::kable(
    caption = "Trust scale labels and item names") %>%
  kable_styling() %>%
  scroll_box(height = "300px")

# PRQC -------------------------------------------------------------------------
prqc <- data.frame(
  var_old = names(dat_w1)[grepl("QPRQC", names(dat_w1))],
  var_new = paste0("prqc_", 1:18),
  labels = str_remove(
    str_remove(
      var_label(dat_w1[,grepl("QPRQC", names(dat_w1))], unlist = T),
      "General.*"),
    "[^.]*\\."),
  row.names = NULL
)

# scale scores
prqc <- prqc %>%
  mutate(subscale = case_when(
    grepl("_1$|_7$|_13$", var_new) ~ "satisfaction",
    grepl("_2$|_8$|_14$", var_new) ~ "commitment",
    grepl("_3$|_9$|_15$", var_new) ~ "intimacy",
    grepl("_4$|_10$|_16$", var_new) ~ "trust",
    grepl("_5$|_11$|_17$", var_new) ~ "passion",
    grepl("_6$|_12$|_18$", var_new) ~ "love"))

prqc %>%
  knitr::kable(
    caption = "PRQC scale labels and item names") %>%
  kable_styling() %>%
  scroll_box(height = "300px")

# RENAMING ---------------------------------------------------------------------

# based on variable names data frames
# demographics and id
names(dat_w1)[match(basics$var_old, names(dat_w1))] <- basics$var_new
names(dat_w2)[match(basics$var_old[1], names(dat_w2))] <- basics$var_new[1]
names(dat_w3)[match(basics$var_old[1], names(dat_w3))] <- basics$var_new[1]

# bfas self
names(dat_w1)[match(bfas_self$var_old, names(dat_w1))] <- bfas_self$var_new
names(dat_w2)[match(bfas_fu$var_old, names(dat_w2))] <- bfas_fu$var_new
names(dat_w3)[match(bfas_fu$var_old, names(dat_w3))] <- bfas_fu$var_new

# all other scales
names(dat_w1)[match(bfas_partner$var_old, names(dat_w1))] <- bfas_partner$var_new
names(dat_w1)[match(aaq$var_old, names(dat_w1))] <- aaq$var_new
names(dat_w1)[match(resp$var_old, names(dat_w1))] <- resp$var_new
names(dat_w1)[match(trust$var_old, names(dat_w1))] <- trust$var_new
names(dat_w1)[match(prqc$var_old, names(dat_w1))] <- prqc$var_new
names(dat_w2)[match(bfas_partner$var_old, names(dat_w2))] <- bfas_partner$var_new
names(dat_w2)[match(aaq$var_old, names(dat_w2))] <- aaq$var_new
names(dat_w2)[match(resp$var_old, names(dat_w2))] <- resp$var_new
names(dat_w2)[match(trust$var_old, names(dat_w2))] <- trust$var_new
names(dat_w2)[match(prqc$var_old, names(dat_w2))] <- prqc$var_new
names(dat_w3)[match(bfas_partner$var_old, names(dat_w3))] <- bfas_partner$var_new
names(dat_w3)[match(aaq$var_old, names(dat_w3))] <- aaq$var_new
names(dat_w3)[match(resp$var_old, names(dat_w3))] <- resp$var_new
names(dat_w3)[match(trust$var_old, names(dat_w3))] <- trust$var_new
names(dat_w3)[match(prqc$var_old, names(dat_w3))] <- prqc$var_new

# select only relevant variables
dat_w1 <- dat_w1 %>%
  select(all_of(c(basics$var_new, bfas_self$var_new, bfas_partner$var_new, 
                  aaq$var_new, resp$var_new, trust$var_new, prqc$var_new)))
dat_w2 <- dat_w2 %>%
  select(all_of(c(basics$var_new[1], bfas_fu$var_new, bfas_partner$var_new, 
                  aaq$var_new, resp$var_new, trust$var_new, prqc$var_new)))
dat_w3 <- dat_w3 %>%
  select(all_of(c(basics$var_new[1], bfas_fu$var_new, bfas_partner$var_new, 
                  aaq$var_new, resp$var_new, trust$var_new, prqc$var_new)))
```


### 2. Descriptives: Scale scoring and summary statistics

```{r score}
# reverse scores ---------------------------------------------------------------
# pull out reversed items for each scale
reverse_bfas_w1 <- c(
  bfas_self[bfas_self$keys == -1, "var_new"],
  bfas_partner[bfas_partner$keys == -1, "var_new"]
)
reverse_bfas_fu <- c(
  bfas_fu[bfas_fu$keys == -1, "var_new"],
  bfas_partner[bfas_partner$keys == -1, "var_new"]
)
reverse_aaq <- aaq[aaq$keys == -1, "var_new"]
# reverse scores
dat_w1[, reverse_bfas_w1] <- 6 - dat_w1[, reverse_bfas_w1]
dat_w2[, reverse_bfas_fu] <- 6 - dat_w2[, reverse_bfas_fu]
dat_w3[, reverse_bfas_fu] <- 6 - dat_w3[, reverse_bfas_fu]
dat_w1[, reverse_aaq] <- 8 - dat_w1[, reverse_aaq]
dat_w2[, reverse_aaq] <- 8 - dat_w2[, reverse_aaq]
dat_w3[, reverse_aaq] <- 8 - dat_w3[, reverse_aaq]

# BFAS -------------------------------------------------------------------------
for(var in unique(bfas_self$subscale)) {
  
  ### wave 1 ###
  
  # pull out item variables
  self_items <- bfas_self[bfas_self$subscale == var, "var_new"]
  self_df <- dat_w1[, names(dat_w1) %in% self_items]
  partner_items <- bfas_partner[bfas_partner$subscale == var, "var_new"]
  partner_df <- dat_w1[, names(dat_w1) %in% partner_items]
  
  # create and append scale scores
  assign(x = var, value = rowMeans(self_df, na.rm = T))
  dat_w1[var] <- get(var)
  assign(x = paste0(var, "_partner"), value = rowMeans(partner_df, na.rm = T))
  dat_w1[paste0(var, "_partner")] <- get(paste0(var, "_partner"))
  
  ### wave 2 and 3 ### 
  self_items_fu <- bfas_fu[bfas_fu$subscale == var, "var_new"]
  self_df_w2 <- dat_w2[, names(dat_w2) %in% self_items_fu]
  self_df_w3 <- dat_w3[, names(dat_w3) %in% self_items_fu]
  partner_df_w2 <- dat_w2[, names(dat_w2) %in% partner_items]
  partner_df_w3 <- dat_w3[, names(dat_w3) %in% partner_items]

  # create and append scale scores
  assign(x = var, value = rowMeans(self_df_w2, na.rm = T))
  dat_w2[var] <- get(var)
  assign(x = var, value = rowMeans(self_df_w3, na.rm = T))
  dat_w3[var] <- get(var)
  assign(x = paste0(var, "_partner"), value = rowMeans(partner_df_w2, na.rm = T))
  dat_w2[paste0(var, "_partner")] <- get(paste0(var, "_partner"))
  assign(x = paste0(var, "_partner"), value = rowMeans(partner_df_w3, na.rm = T))
  dat_w3[paste0(var, "_partner")] <- get(paste0(var, "_partner"))
}

# AAQ --------------------------------------------------------------------------
for (var in unique(aaq$subscale)) {
  
  # pull out item variables
  aaq_items <- aaq[aaq$subscale == var, "var_new"]
  aaq_df <- dat_w1[, names(dat_w1) %in% aaq_items]
  aaq_df_w2 <- dat_w2[, names(dat_w2) %in% aaq_items]
  aaq_df_w3 <- dat_w3[, names(dat_w3) %in% aaq_items]
  
  # create and append scale scores
  assign(x = var, value = rowMeans(aaq_df, na.rm = T))
  dat_w1[var] <- get(var)
  assign(x = var, value = rowMeans(aaq_df_w2, na.rm = T))
  dat_w2[var] <- get(var)
  assign(x = var, value = rowMeans(aaq_df_w3, na.rm = T))
  dat_w3[var] <- get(var)
}

# Responsiveness ---------------------------------------------------------------
# wave 1
resp_items <- resp$var_new
resp_df <- dat_w1[, names(dat_w1) %in% resp_items]
assign(x = "resp_scale", value = rowMeans(resp_df, na.rm = T))
dat_w1["resp"] <- resp_scale
# wave 2
resp_df_w2 <- dat_w2[, names(dat_w2) %in% resp_items]
assign(x = "resp_scale", value = rowMeans(resp_df_w2, na.rm = T))
dat_w2["resp"] <- resp_scale
# wave 3
resp_df_w3 <- dat_w3[, names(dat_w3) %in% resp_items]
assign(x = "resp_scale", value = rowMeans(resp_df_w3, na.rm = T))
dat_w3["resp"] <- resp_scale

# Trust ------------------------------------------------------------------------
# wave 1
trust_items <- trust$var_new
trust_df <- dat_w1[, names(dat_w1) %in% trust_items]
assign(x = "trust_scale", value = rowMeans(trust_df, na.rm = T))
dat_w1["trust"] <- trust_scale
# wave 2
trust_df_w2 <- dat_w2[, names(dat_w2) %in% trust_items]
assign(x = "trust_scale", value = rowMeans(trust_df_w2, na.rm = T))
dat_w2["trust"] <- trust_scale
# wave 3
trust_df_w3 <- dat_w3[, names(dat_w3) %in% trust_items]
assign(x = "trust_scale", value = rowMeans(trust_df_w3, na.rm = T))
dat_w3["trust"] <- trust_scale

# PRQC -------------------------------------------------------------------------
for (var in unique(prqc$subscale)) {
  
  # pull out item variables
  prqc_items <- prqc[prqc$subscale == var, "var_new"]
  prqc_df <- dat_w1[, names(dat_w1) %in% prqc_items]
  prqc_df_w2 <- dat_w2[, names(dat_w2) %in% prqc_items]
  prqc_df_w3 <- dat_w3[, names(dat_w3) %in% prqc_items]
  
  # create and append scale scores
  assign(x = paste0("prqc_",var), value = rowMeans(prqc_df, na.rm = T))
  dat_w1[paste0("prqc_",var)] <- get(paste0("prqc_",var))
  assign(x = paste0("prqc_",var), value = rowMeans(prqc_df_w2, na.rm = T))
  dat_w2[paste0("prqc_",var)] <- get(paste0("prqc_",var))
  assign(x = paste0("prqc_",var), value = rowMeans(prqc_df_w3, na.rm = T))
  dat_w3[paste0("prqc_",var)] <- get(paste0("prqc_",var))
}
```

To conform to the data structure required for the analytic scripts, the data will be combined into a long dataframe across 3 waves, with `time` denoting the timepoint, then transformed to a wider structure, with each row representing a couple at a specific time point, instead of a participant at a specific time point as the data structure shown here in this descriptive report. The suffix `_1` denotes a female participant, and `_2` denotes a male participant.

```{r merge}
# select only demographics and scale scores
dat_w1 <- dat_w1 %>%
  select(all_of(c(basics$var_new, bfas_self$subscale, 
                  paste0(bfas_partner$subscale, "_partner"),
                  aaq$subscale, "resp", "trust", 
                  paste0("prqc_", prqc$subscale))))
dat_w2 <- dat_w2 %>%
select(all_of(c(basics$var_new[1], bfas_self$subscale, 
                  paste0(bfas_partner$subscale, "_partner"),
                  aaq$subscale, "resp", "trust", 
                  paste0("prqc_", prqc$subscale))))
dat_w3 <- dat_w3 %>%
select(all_of(c(basics$var_new[1], bfas_self$subscale, 
                  paste0(bfas_partner$subscale, "_partner"),
                  aaq$subscale, "resp", "trust", 
                  paste0("prqc_", prqc$subscale))))

# merge in demographics
dat_w2 <- merge(dat_w1[c(basics$var_new)], dat_w2, all.y = T)
dat_w3 <- merge(dat_w1[c(basics$var_new)], dat_w3, all.y = T)

# merge in couple IDs
dat_w1 <- merge(ids, dat_w1, all.y = T)
dat_w2 <- merge(ids, dat_w2, all.y = T)
dat_w3 <- merge(ids, dat_w3, all.y = T)

# only keep data when both partners are present
full_ids <- na.omit(dat_w1$couple[duplicated(dat_w1$couple)])
dat_w1 <- dat_w1 %>%
  filter(couple %in% full_ids)
full_ids_w2 <- na.omit(dat_w2$couple[duplicated(dat_w2$couple)])
dat_w2 <- dat_w2 %>%
  filter(couple %in% full_ids_w2)
full_ids_w3 <- na.omit(dat_w3$couple[duplicated(dat_w3$couple)])
dat_w3 <- dat_w3 %>%
  filter(couple %in% full_ids_w3)

# add time variable
dat_w1 <- dat_w1 %>%
  mutate(time = 0) %>%
  relocate(time) %>%
  # only keep non-missing sex
  # only removing 2 cases who also have entirely missing data
  filter(!is.na(sex)) %>%
  # filter out same-gender couples and missing-gender couples
  filter(!couple %in% c(4951, 4968, 4991, 5000, 5013))
dat_w2 <- dat_w2 %>%
  mutate(time = 8) %>%
  relocate(time) %>%
  # only keep non-missing sex
  # only removing 2 cases who also have entirely missing data
  filter(!is.na(sex)) %>%
  # filter out same-gender couples and missing-gender couples
  filter(!couple %in% c(4951, 4968, 4991, 5000, 5013))
dat_w3 <- dat_w3 %>%
  mutate(time = 16) %>%
  relocate(time) %>%
  # only keep non-missing sex
  # only removing 2 cases who also have entirely missing data
  filter(!is.na(sex)) %>%
  # filter out same-gender couples and missing-gender couples
  filter(!couple %in% c(4951, 4968, 4991, 5000, 5013))

# long datasets of all time points
dat_long <- rbind(dat_w1, dat_w2, dat_w3) %>% select(-ID)

# fix couple IDs to range from 0 to 1
id_df <- data.frame(
  id_old = sort(unique(dat_w1$couple)),
  id_new = 1:length(unique(dat_w1$couple))
)
for(id in 1:nrow(id_df)) {
  dat_long$couple[dat_long$couple == id_df$id_old[id]] <- id_df$id_new[id]
}

# pivot_wider for 1 couple at 1 time per row
dat_analytic <- dat_long %>%
  pivot_wider(id_cols = c("couple", "time"),
              names_from = "sex",
              values_from = names(dat_long)[!names(dat_long) %in% c("couple", "sex", "time")])

# save data file
#rio::export(dat_analytic, 
#            paste0(here(), "/data/cleaned_data_yw.RDS"))

```

```{r descr}
# demographics
dat_w1 %>% 
  select("age", "ethnic_black", "ethnic_asian", "ethnic_white", "ethnic_hisp") %>%
  descr(stats = "common", order = "p") %>%
  knitr::kable(caption = "Descriptives of demographic variables") %>%
  kable_styling()

# scale scores wave 1
dat_w1 %>%
  select(-c("sex", "age", "time",
            "ethnic_black", "ethnic_asian", "ethnic_white", "ethnic_hisp")) %>%
  descr(stats = "common", order = "p") %>%
  knitr::kable(caption = "Descriptives of scale scores at wave 1") %>%
  kable_styling() %>%
  scroll_box(height = "300px")

# scale scores wave 2
dat_w2 %>%
  select(-c("sex", "age", "time",
            "ethnic_black", "ethnic_asian", "ethnic_white", "ethnic_hisp")) %>%
  descr(stats = "common", order = "p") %>%
  knitr::kable(caption = "Descriptives of scale scores at wave 2") %>%
  kable_styling() %>%
  scroll_box(height = "300px")

# scale scores wave 3
dat_w3 %>%
  select(-c("sex", "age", "time",
            "ethnic_black", "ethnic_asian", "ethnic_white", "ethnic_hisp")) %>%
  descr(stats = "common", order = "p") %>%
  knitr::kable(caption = "Descriptives of scale scores at wave 3") %>%
  kable_styling() %>%
  scroll_box(height = "300px")
```

