---
title: 'Longitudinal Assortative Mating Results: Early Dating'
author: "Linh Nguyen"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: no
    code_folding: hide
    css: styles.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r libraries, warning=FALSE, message=FALSE}
library(here)        # for file directory
library(tidyr)       # for pivot_wider
library(rio)         # to load in data
library(dplyr)       # general wrangling
library(brms)        # longitudinal similarity
library(rempsyc)     # simple slopes analysis
library(Hmisc)       # correlation matrix
library(psych)       # fisher's z transformation
library(lme4)        # linear mixed model   
library(lmerTest)    # linear mixed model significance test
library(lavaan)      # RI-CLPM
library(semPlot)     # semPaths
library(kableExtra)  # for styling and scroll_box

# source the helper file
source("00_helpers.R")

options(digits = 3)
```

# Meta Data

This is the analytic report for the Early Dating dataset.

- Online access: This analytic report is published on [RPubs](https://rpubs.com/nguyenllpsych/longassort-results-01).
- Preregistration document: [RPubs](https://rpubs.com/nguyenllpsych/diss-03-prereg).
- Descriptives and exploratory data analysis on the Early Dating analytic dataset: [RPubs](https://rpubs.com/nguyenllpsych/longassort-descr-01).


```{r dat}
# load in data
data_yw <- rio::import(paste0(here(), "/data/cleaned_data_yw.RDS"))

# example data
data_yw %>%
  arrange(couple) %>%
  head() %>% 
  knitr::kable(
    caption = "Example first 6 rows of the Early Dating dataset"
  ) %>% 
  kableExtra::kable_styling() %>%
  scroll_box(height = "300px")
```

# Missingness Analysis

```{r missing, results="asis"}
miss_analysis(ID = "couple", var = c("agreeableness_self_1", "agreeableness_self_2"), 
              var_demo = c(
                paste0(rep(c("ethnic_black_", "ethnic_asian_", "ethnic_white_", 
                             "ethnic_hisp_", "ethnic_other_"), each = 2), 
                       rep(c(1,2), times = 5)),
                "age_1", "age_2",
                "duration_1", "duration_2",
                paste0(rep(c("agreeableness_self_", "conscientiousness_self_", 
                             "extraversion_self_", "neuroticism_self_", "openness_self_"), 
                           each = 2),
                       rep(c(1,2), times = 5))
              ),
              var_rela = 
                paste0(rep(c("prqc_overall_", "avoidance_", "anxiety_",
                             "resp_", "trust_"), each = 2),
                       rep(c(1,2), times = 5)),
              data = data_yw)
```

# Supplemental Analysis - Relationship Duration

These analyses examined whether relationship duration is associated with relationship quality

```{r rela-duration}
cor.test(data_yw[data_yw$time==0,]$prqc_overall_1, 
         data_yw[data_yw$time==0,]$duration_1)
cor.test(data_yw[data_yw$time==0,]$prqc_overall_2,
         data_yw[data_yw$time==0,]$duration_2)
```


# Research Question 1. Evidence of Assortative Mating

## H1. Baseline similarity

#### At baseline, romantic partners are similar in their personality such that their scale scores are significantly and positively correlated

```{r H1, results="asis"}
var_list <- c(
  # traits
  paste0(
    c("neuroticism", "agreeableness", "conscientiousness", "extraversion", "openness"),
    "_self"),
  
  # CA
  "avoidance", "anxiety", "resp", "trust",
  
  # relationship quality - not for hypothesis testing, just for slope later
  "prqc_overall"
)

prof_list <- data.frame(
  bigfive = paste0(
    c("neuroticism", "agreeableness", "conscientiousness", "extraversion", "openness"),
    "_self")
)

# run function for h1
h1_results <- h1_function(var_list = var_list, prof_list = prof_list, 
                          df = data_yw[which(data_yw$time == 0),], time = 0)

# results
h1_results$bivariate %>% 
  filter(variable != "prqc_overall") %>%
  knitr::kable(caption = "Bivariate between-partner correlation") %>% 
  kableExtra::kable_styling() %>%
  scroll_box(height = "300px")

h1_results$profile %>% 
  knitr::kable(caption = "Proportion of signficant between-partner profile correlations in traits") %>% 
  kableExtra::kable_styling()

data_yw <- merge(data_yw, h1_results$profile_df, all = TRUE)

summary(data_yw %>%
          filter(time == 0) %>%
          select(starts_with("bigfive"))) %>% 
  knitr::kable(caption = "Descriptive summary of trait profile correlations at baseline") %>% 
  kableExtra::kable_styling()
```

## H2. Difference in correlations

#### At baseline, romantic partners are more similar in their characteristic adaptations than in their personality traits.

```{r H2}
# run function on simulated data
h2_function(cor_tab = h1_results$bivariate) %>% 
  filter(V1 != "prqc_overall" & V2 != "prqc_overall") %>%
  arrange(desc(abs(z_stat))) %>%
  knitr::kable(caption = "Comparisons of bivariate correlations of personality traits vs CAs") %>% 
  kableExtra::kable_styling() %>%
  scroll_box(height = "300px")
```

## H3. Longitudinal similarity

#### Longitudinally, romantic partners show a similar change trajectory in self-reported personality across the study duration such that their slopes are significantly and positively correlated.

```{r H3}
var_list <- c(
  paste0(
    c("agreeableness", "conscientiousness", "extraversion", "openness", "neuroticism"),
    rep(c("_self", "_partner"), each = 5)),
  "avoidance", "anxiety", "resp", "trust",
  "prqc_overall"
)

# run function
h3_results <- h3_function(var_list = var_list, df = data_yw,
                          dir = paste0(here(), "/results/yw/brm"))

# view longitudinal trends
h3_results$slopes_tab %>% 
  knitr::kable(caption = "Longitudinal trends in all variables") %>% 
  kableExtra::kable_styling() %>%
  scroll_box(height = "300px")

# view longitudinal similarity 
h3_results$results_df %>% 
  knitr::kable(caption = "Bivariate between-partner slope correlations") %>% 
  kableExtra::kable_styling() %>%
  scroll_box(height = "300px")

# merge slope data to original dataframe
slope_df <- h3_results$slope_df %>%
  mutate(time = 0)
data_yw <- merge(data_yw,
                 slope_df,
                 all = T)
```

## H4. Perceived/actual similarity comparison 

#### At baseline, perceived similarity in personality traits and characteristic adaptations is stronger than actual similarity. That is, the correlation between each partner’s self-perception and perception of their partner is stronger than the correlation between two partners’ self-perceptions.

```{r H4}
perception_list <- c("neuroticism", "agreeableness", "conscientiousness", "extraversion", "openness")

# run function
h4_results <- h4_function(perception_list = perception_list,
                          time = 0, df = data_yw)

h4_results$similarity_df %>%
  knitr::kable(
    caption = "Actual and perceived similarities as bivariate correlations") %>%
  kableExtra::kable_styling() %>%
  scroll_box(height = "300px")

h4_results$compare_df %>%
  knitr::kable(
    caption = "Comparison between actual and perceived similarities") %>%
  kableExtra::kable_styling() %>%
  scroll_box(height = "300px")
```


# Research Question 2. Benefit of Assortative Mating

## H5. Baseline benefit

#### At baseline, partner similarity in self-reported personality is associated with enhanced relationship quality.

```{r h5}
var_list <- c(
  # traits
  paste0(
    c("neuroticism", "agreeableness", "conscientiousness", "extraversion", "openness"),
    "_self"),
  # CA
  "avoidance", "anxiety", "resp", "trust"
)
quality_list <- "prqc_overall"

# run function
drsa_results <- drsa_function(var_list = var_list,
                              quality_list = quality_list,
                              dir = paste0(here(), "/results/yw/drsa"),
                              df = data_yw)

# output results
drsa_results$est_df %>% 
  mutate(across(is.numeric, round, digits=2)) %>%
  knitr::kable(caption = "All estimates for DRSA auxiliary parameters") %>% 
  kableExtra::kable_styling() %>%
  scroll_box(height = "300px")

drsa_results$results_df %>% 
  knitr::kable(caption = "DRSA congruence results") %>% 
  kableExtra::kable_styling() %>%
  scroll_box(height = "300px")
```

## H6. Longitudinal benefit

#### Longitudinally, partner similarity in change trajectories of self-reported personality is associated with higher average relationship quality

```{r h6}
# create dataframe of average relationship quality across time
data_yw_drsalong <- data_yw %>%
  group_by(couple) %>%
  mutate(prqc_overall_avg_1 = mean(prqc_overall_1, na.rm=T),
         prqc_overall_avg_2 = mean(prqc_overall_2, na.rm=T)) %>%
  ungroup() %>%
  filter(time == 0)

# params for longitudinal drsa models
var_list <- c(
  # traits
  paste0(
    "slope_",
    c("neuroticism", "agreeableness", "conscientiousness", "extraversion", "openness"),
    "_self"),
  # CA
  paste0("slope_", c("avoidance", "anxiety", "resp", "trust"))
)
quality_list <- "prqc_overall_avg"

# run function
drsa_long_results <- drsa_function(var_list = var_list,
                                   quality_list = quality_list,
                                   dir = paste0(here(), "/results/yw/drsa_long"),
                                   df = data_yw_drsalong,
                                   scale = T)

# output results
drsa_long_results$est_df %>% 
  mutate(across(is.numeric, round, digits=2)) %>%
  knitr::kable(caption = "All estimates for DRSA auxiliary parameters") %>% 
  kableExtra::kable_styling() %>%
  scroll_box(height = "300px")

drsa_long_results$results_df %>% 
  knitr::kable(caption = "DRSA congruence results") %>% 
  kableExtra::kable_styling() %>%
  scroll_box(height = "300px")
```