---
title: "Longitudinal Assortative Mating Results: Transition to Parenthood"
author: "Linh Nguyen"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: false
    code_folding: 'hide'
    css: styles.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r libraries, warning=FALSE, message=FALSE}
library(here)        # for file directory
library(tidyr)       # for pivot_wider
library(rio)         # to load in data
library(dplyr)       # general wrangling
library(brms)        # longitudinal similarity
library(rempsyc)     # simple slopes analysis
library(Hmisc)       # correlation matrix
library(psych)       # fisher's z transformation
library(lme4)        # linear mixed model   
library(lmerTest)    # linear mixed model significance test
library(lavaan)      # RI-CLPM
library(semPlot)     # semPaths
library(kableExtra)  # for styling and scroll_box
library(RSA)         # for plotting DRSA

# source the helper file
source("00_helpers.R")
```

# Meta Data

This is the analytic report for the Transition to Parenthood dataset.

- Online access: This analytic report is published on [RPubs](https://rpubs.com/nguyenllpsych/longassort-results-02).
- Preregistration document: [RPubs](https://rpubs.com/nguyenllpsych/diss-03-prereg).
- Descriptives and exploratory data analysis on the Transition to Parenthood analytic dataset: [RPubs](https://rpubs.com/nguyenllpsych/longassort-descr-02).


```{r dat}
# load in data
data_ttp <- rio::import(paste0(here(), "/data/cleaned_data_ttp.RDS"))

# example data
head(data_ttp) %>% 
  knitr::kable(
    caption = "Example first 6 rows of the Transition to Parenthood dataset"
  ) %>% 
  kableExtra::kable_styling() %>%
  scroll_box(height = "300px")
```

# Missingness Analysis

```{r missing, results="asis"}
miss_analysis(ID = "couple", var = c("ecr_avoid_1", "ecr_avoid_2"), 
              var_demo = c("P1Aage_1", "P1Aage_2", "P1Arace_1", "P1Arace_2",
                           "P1Aeducate_1", "P1Aeducate_2",
                           "P1Aincome_1", "P1Aincome_2",
                           "P1Altotalmo_1", "P1Altotalmo_2",
                           "bfi_o_1", "bfi_c_1", "bfi_e_1", "bfi_a_1", "bfi_n_1",
                           "bfi_o_2", "bfi_c_2", "bfi_e_2", "bfi_a_2", "bfi_n_2"), 
              var_rela = paste0(rep(c("das_satis_", "das_coh_",
                                      "ecr_avoid_", "ecr_anx_",
                                      "ss_self_", "sp_self_",
                                      "ks_prox_self_", "ks_sens_self_",
                                      "ks_coop_self_", "ks_comp_self_",
                                      "con_collab_self_", "con_capit_self_", 
                                      "con_stale_self_", "con_verba_self_"), each = 2),
                                rep(c(1,2), times = 14)),
              data = data_ttp)
```


# Supplemental Analysis - Relationship Duration

These analyses examined whether relationship duration is associated with relationship quality

```{r rela-duration}
cor.test(data_ttp[data_ttp$time==0,]$das_satis_1, 
         data_ttp[data_ttp$time==0,]$P1Amtotalmo_1)
cor.test(data_ttp[data_ttp$time==0,]$das_satis_2, 
         data_ttp[data_ttp$time==0,]$P1Amtotalmo_2)
cor.test(data_ttp[data_ttp$time==0,]$das_coh_1, 
         data_ttp[data_ttp$time==0,]$P1Amtotalmo_1)
cor.test(data_ttp[data_ttp$time==0,]$das_coh_2, 
         data_ttp[data_ttp$time==0,]$P1Amtotalmo_2)
```


# Research Question 1. Evidence of Assortative Mating

## H1. Baseline similarity

#### At baseline, romantic partners are similar in their personality such that their scale scores are significantly and positively correlated

```{r H1, results="asis"}
var_list <- c(
  # traits
  "bfi_e", "bfi_a", "bfi_c", "bfi_n", "bfi_o",
  
  # CA
  "ecr_avoid", "ecr_anx", 
  "ss_self", "ss_partner", "sp_self", "sp_partner",
  "ks_prox_self", "ks_prox_partner", "ks_sens_self", "ks_sens_partner",
  "ks_coop_self", "ks_coop_partner", "ks_comp_self", "ks_comp_partner",
  "con_collab_self", "con_collab_partner", "con_capit_self", "con_capit_partner",
  "con_stale_self", "con_stale_partner", "con_verba_self", "con_verba_partner",
  
  # relationship quality - not for hypothesis testing, just for slope later
  "das_satis", "das_coh"
)

prof_traits_list <- data.frame(
  bigfive = c("bfi_e", "bfi_a", "bfi_c", "bfi_n", "bfi_o")
  
)
prof_ca_list <- data.frame(
  conflict = c("con_collab_self", "con_collab_partner", 
               "con_capit_self", "con_capit_partner",
               "con_stale_self", "con_stale_partner", 
               "con_verba_self", "con_verba_partner"),
  care = c("ks_prox_self", "ks_prox_partner", "ks_sens_self", "ks_sens_partner",
           "ks_coop_self", "ks_coop_partner", "ks_comp_self", "ks_comp_partner")
)

# run function for h1
h1_bivar <- h1_function(var_list = var_list, prof_list = NULL, 
                        df = data_ttp, time = 0)
h1_prof_traits <- h1_function(var_list = NULL, prof_list = prof_traits_list,
                              df = data_ttp[which(data_ttp$time == 0),])
h1_prof_ca <- h1_function(var_list = NULL, prof_list = prof_ca_list,
                          df = data_ttp)

# results
h1_bivar$bivariate %>% 
  filter(!grepl("das_", variable)) %>%
  knitr::kable(caption = "Bivariate between-partner correlation") %>% 
  kableExtra::kable_styling() %>%
  scroll_box(height = "300px")

h1_prof_traits$profile %>% 
  knitr::kable(caption = "Proportion of signficant between-partner profile correlations in traits") %>% 
  kableExtra::kable_styling()

h1_prof_ca$profile %>% 
  knitr::kable(caption = "Proportion of signficant between-partner profile correlations in CAs") %>% 
  kableExtra::kable_styling()

data_ttp <- merge(data_ttp, h1_prof_traits$profile_df, all = TRUE)
data_ttp <- merge(data_ttp, h1_prof_ca$profile_df, all = TRUE)
data_ttp <- merge(data_ttp, h1_prof_ca$profile_df, all = TRUE)

summary(data_ttp %>%
          filter(time == 0) %>%
          select(starts_with("bigfive"))) %>% 
  knitr::kable(caption = "Descriptive summary of trait profile correlations at baseline") %>% 
  kableExtra::kable_styling()

for(timepoint in sort(unique(data_ttp$time))) {
  summary(data_ttp %>%
            filter(time == timepoint) %>%
            select(starts_with(c("conflict", "care")))) %>% 
    knitr::kable(caption = paste("Descriptive summary of CA profile correlations at time =", timepoint)) %>% 
    kableExtra::kable_styling() %>%
    print()
}
```

## H2. Difference in correlations

#### At baseline, romantic partners are more similar in their characteristic adaptations than in their personality traits.

```{r H2}
# run function on simulated data
h2_function(cor_tab = h1_bivar$bivariate) %>% 
  filter(!grepl("das_", V1) & !grepl("das_", V2)) %>%
  arrange(desc(abs(z_stat))) %>%
  knitr::kable(caption = "Comparisons of bivariate correlations of personality traits vs CAs") %>% 
  kableExtra::kable_styling() %>%
  scroll_box(height = "300px")
```

## H3. Longitudinal similarity

#### Longitudinally, romantic partners show a similar change trajectory in self-reported personality across the first two years of parenthood such that their slopes are significantly and positively correlated.

```{r H3}
var_list <- c("ecr_avoid", "ecr_anx",
              "ss_self", "ss_partner", "sp_self", "sp_partner",
              "ks_prox_self", "ks_prox_partner", "ks_sens_self", "ks_sens_partner",
              "ks_coop_self", "ks_coop_partner", "ks_comp_self", "ks_comp_partner",
              "con_collab_self", "con_collab_partner", "con_capit_self", "con_capit_partner",
              "con_stale_self", "con_stale_partner", "con_verba_self", "con_verba_partner",
              "das_satis", "das_coh"
)

# run function
h3_results <- h3_function(var_list = var_list, df = data_ttp,
                          dir = paste0(here(), "/results/ttp/brm"))

# view longitudinal trends
h3_results$slopes_tab %>% 
  knitr::kable(caption = "Longitudinal trends in all variables") %>% 
  kableExtra::kable_styling() %>%
  scroll_box(height = "300px")

# view longitudinal similarity 
h3_results$results_df %>% 
  knitr::kable(caption = "Bivariate between-partner slope correlations") %>% 
  kableExtra::kable_styling() %>%
  scroll_box(height = "300px")

# merge slope data to original dataframe
slope_df <- h3_results$slope_df %>%
  mutate(time = 0)
data_ttp <- merge(data_ttp,
                  slope_df,
                  all = T)
```

## H4. Perceived/actual similarity comparison 

#### At baseline, perceived similarity in personality traits and characteristic adaptations is stronger than actual similarity. That is, the correlation between each partner’s self-perception and perception of their partner is stronger than the correlation between two partners’ self-perceptions.

```{r h4}
perception_list <- c(
  "ss", "sp",
  "ks_prox", "ks_sens",
  "ks_coop", "ks_comp",
  "con_collab", "con_capit",
  "con_stale", "con_verba"
)

# run function
h4_results <- h4_function(perception_list = perception_list,
                          time = 0, df = data_ttp)

h4_results$similarity_df %>%
  knitr::kable(
    caption = "Actual and perceived similarities as bivariate correlations") %>%
  kableExtra::kable_styling() %>%
  scroll_box(height = "300px")

h4_results$compare_df %>%
  knitr::kable(
    caption = "Comparison between actual and perceived similarities") %>%
  kableExtra::kable_styling() %>%
  scroll_box(height = "300px")
```

# Research Question 2. Benefit of Assortative Mating

## H5. Baseline benefit

#### At baseline, partner similarity in self-reported personality is associated with enhanced relationship quality.

```{r h5}
var_list <- c(
  # traits
  "bfi_e", "bfi_a", "bfi_c", "bfi_n", "bfi_o",
  
  # CA
  "ecr_avoid", "ecr_anx", 
  "ss_self", "sp_self",
  "ks_prox_self", "ks_sens_self",
  "ks_coop_self", "ks_comp_self",
  "con_collab_self", "con_capit_self",
  "con_stale_self",  "con_verba_self"
)

quality_list <- c("das_satis", "das_coh")

# run function
drsa_results <- drsa_function(var_list = var_list,
                              quality_list = quality_list,
                              dir = paste0(here(), "/results/ttp/drsa"),
                              df = data_ttp)

# output results
drsa_results$est_df %>% 
  mutate(across(is.numeric, round, digits=2)) %>%
  knitr::kable(caption = "All estimates for DRSA auxiliary parameters") %>% 
  kableExtra::kable_styling() %>%
  scroll_box(height = "300px")

drsa_results$results_df %>% 
  knitr::kable(caption = "DRSA congruence results") %>% 
  kableExtra::kable_styling() %>%
  scroll_box(height = "300px")
```

## H6. Longitudinal benefit

#### Longitudinally, partner similarity in change trajectories of self-reported personality is associated with higher average relationship quality.

```{r drsa-long}
# create dataframe of average relationship quality across time
data_ttp_drsalong <- data_ttp %>%
  group_by(couple) %>%
  mutate(das_coh_avg_1 = mean(das_coh_1, na.rm=T),
         das_coh_avg_2 = mean(das_coh_2, na.rm=T),
         das_satis_avg_1 = mean(das_satis_1, na.rm=T),
         das_satis_avg_2 = mean(das_satis_2, na.rm=T)) %>%
  ungroup() %>%
  filter(time == 0)

# params for longitudinal drsa models
var_list <- paste0("slope_",
                   c("ecr_avoid", "ecr_anx", 
                     "ss_self", "sp_self",
                     "ks_prox_self", "ks_sens_self",
                     "ks_coop_self", "ks_comp_self",
                     "con_collab_self", "con_capit_self",
                     "con_stale_self",  "con_verba_self"))

quality_list <- c("das_satis_avg", "das_coh_avg")

# run function
drsa_long_results <- drsa_function(var_list = var_list,
                                   quality_list = quality_list,
                                   dir = paste0(here(), "/results/ttp/drsa_long"),
                                   df = data_ttp_drsalong,
                                   scale = T)

# output results
drsa_long_results$est_df %>% 
  mutate(across(is.numeric, round, digits=2)) %>%
  knitr::kable(caption = "All estimates for DRSA auxiliary parameters") %>% 
  kableExtra::kable_styling() %>%
  scroll_box(height = "300px")

drsa_long_results$results_df %>% 
  knitr::kable(caption = "DRSA congruence results") %>% 
  kableExtra::kable_styling() %>%
  scroll_box(height = "300px")
```

#### Plot DRSA

There was 1 model for which a broad congruence pattern was found: longitudinal similarity on caregiving Proximity v. Distance on Dyadic Cohesion.

The dyadic response surface analysis plot of these associations are presented below:

```{r drsa-long-plot}
# load model
mod <- readRDS(paste0(
  here(), "/results/ttp/drsa_long/slope_ks_prox_self_das_coh_avg.RDS"))
coefs <- as.data.frame(unclass(standardizedSolution(mod))) %>%
  select(label, est.std) %>%
  mutate(est.std=round(est.std, 3))

plotRSA(x=coefs[coefs$label=="b1f","est.std"], 
        y=coefs[coefs$label=="b2f","est.std"], 
        x2=coefs[coefs$label=="b3f","est.std"], 
        xy=coefs[coefs$label=="b4f","est.std"], 
        y2=coefs[coefs$label=="b5f","est.std"], 
        xlab="Actor", ylab="Partner", zlab="Outcome", 
        project = c(), axes=c("LOC"), 
        param=TRUE, legend=TRUE, gridsize=10, 
        cex.tickLabel=0.5, cex.axesLabel=1, cex.main=1, border=TRUE, 
        distance=c(1,1,1), bw=TRUE, 
        pal=colorRampPalette(c("#333333", "#888888", "#EEEEEE"))(8), 
        main="Dyadic Response Surface Analysis Plot: Broad Congruence")
```
